\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Final\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the final
demonstration and documentation.  The time period of interest is the time
between Rev 0 and the Final documentation.

\section{Team Meeting Attendance}

\begin{table}[H]
  \centering
  \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Meetings}\\
    \midrule
    Total & 8\\
    Kyle D'Souza & 8\\
    Richard Fan & 8\\
    Mitchell Hynes & 7\\
    Rafeed Iqbal & 5\\
    Akshit Gulia & 8\\
    \bottomrule
  \end{tabular}
\end{table}

There is no exact number, but many of our meetings end up being
unplanned or planned on very short notice, so it is understandable
that there will be a decent number of these where some group members
do not attend simply because we didn't give much heads up about the meeting.

\section{Supervisor/Stakeholder Meeting Attendance}

\begin{table}[H]
  \centering
  \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Meetings}\\
    \midrule
    Total & 1\\
    Kyle D'Souza & 1\\
    Richard Fan & 1\\
    Mitchell Hynes & 1\\
    Rafeed Iqbal & 0\\
    Akshit Gulia & 1\\
    \bottomrule
  \end{tabular}
\end{table}

\section{Lecture Attendance}

\begin{table}[H]
  \centering
  \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Lectures}\\
    \midrule
    Total & 1\\
    Kyle D'Souza & 0\\
    Richard Fan & 1\\
    Mitchell Hynes & 1\\
    Rafeed Iqbal & 0\\
    Akshit Gulia & 1\\
    \bottomrule
  \end{tabular}
\end{table}

\section{TA Document Discussion Attendance}

\begin{table}[H]
  \centering
  \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Lectures}\\
    \midrule
    Total & 1\\
    Kyle D'Souza & 1\\
    Richard Fan & 1\\
    Mitchell Hynes & 1\\
    Rafeed Iqbal & 1\\
    Akshit Gulia & 1\\
    \bottomrule
  \end{tabular}
\end{table}

\section{Commits}

\begin{table}[H]
  \centering
  \begin{tabular}{lll}
    \toprule
    \textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
    \midrule
    Total & 250 & 100\% \\
    Kyle D'Souza & 79 & 31.6\% \\
    Richard Fan & 42 & 16.8\% \\
    Mitchell Hynes & 48 & 19.2\% \\
    Rafeed Iqbal & 57 & 22.8\% \\
    Akshit Gulia & 24 & 9.6\% \\
    \bottomrule
  \end{tabular}
\end{table}

These numbers were obtained from looking at the GitHub contributor
insights and subracting the numbers from the POC demo and Rev0 team
contribution reports.

\section{Issue Tracker}

\begin{table}[H]
  \centering
  \begin{tabular}{lll}
    \toprule
    \textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
    \midrule
    Kyle D'Souza & 36 & 12 \\
    Richard Fan & 2 & 10 \\
    Mitchell Hynes & 13 & 9 \\
    Rafeed Iqbal & 0 & 3 \\
    Akshit Gulia & 5 & 4 \\
    \bottomrule
  \end{tabular}
\end{table}

Used the query in GitHub ``is:issue state:open author:\{person\}
created:\textgreater2025-02-07'', to find issues opened by the person
in the given time frame. Used the query ``is:issue state:closed
author:\{person\} closed:\textgreater2025-02-07'' to find issues
authored by the person, which were closed in the given time frame.
Used the query ``is:issue state:closed assignee:\{person\}
closed:\textgreater2025-02-07'' to find issues assigned to a person,
which were closed in the given time frame.

In terms of issues authored the reason it is so imbalanced is because
generally when assigning work for a deliverable we will all have a
call and Kyle will create issues and assign them to people (but
  we are all agreeing on whats being created and who its being assigned
to). To our knowledge issues can't be co-authored, so it leads to
that disproportionate issue creation statistic.

\section{Additional Metrics}

\subsection{Pull Request (PR) Merges}

\begin{table}[H]
  \centering
  \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{PR's Merged}\\
    \midrule
    Total & 28\\
    Kyle D'Souza & 10\\
    Richard Fan & 8\\
    Mitchell Hynes & 5\\
    Rafeed Iqbal & 3\\
    Akshit Gulia & 2\\
    \bottomrule
  \end{tabular}
\end{table}

Numbers were found using the query ``is:pr is:merged
closed:\textgreater2025-02-07 author:\{person\}''.

This metric takes into account the number of pull requests merged
that a student authored. It can be put off a bit if someone took over
a pull request after it was authored, but our team has not done this
very much, so the statistic should be accurate.

\subsection{Pull Request (PR) Reviews}

\begin{table}[H]
  \centering
  \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{PR's Reviewed}\\
    \midrule
    Kyle D'Souza & 25\\
    Richard Fan & 11\\
    Mitchell Hynes & 2\\
    Rafeed Iqbal & 4\\
    Akshit Gulia & 1\\
    \bottomrule
  \end{tabular}
\end{table}

Numbers were found using the query ``is:pr created:\textgreater2025-02-07
reviewed-by:\{person\} -author:\{person\}''

This metric takes into account the number of pull requests reviewed
by a student which they did not author. The reason for disclusion of
pull requests the student authored is that often reviews by a student
on their own pull request is just responding to a comment, or putting
a small annotation, which is helpful, but is not what we are trying
to gather from this metric.

\end{document}
