\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 0\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the Rev 0
Demo.  The time period of interest is the time between the POC demo and the Rev
0 demo. Our POC Demo was Nov. 15, so the period of interest is Nov. 16, 2024 to
Jan. 29, 2025.

\section{Demo Plans}

For the rev0 demo we will be demonstrating the full feature set of
the SyncMaster application as described in the
\href{https://github.com/Spitgranger/SyncMaster/blob/main/docs/SRS-Volere/SRS.pdf}{SRS}.
We may disclude features related to logging contractor entry/exit
times if there is not enough time to complete these features.

\section{Team Meeting Attendance}

\begin{table}[H]
  \centering
  \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Meetings}\\
    \midrule
    Total & 8\\
    Kyle D'Souza & 8\\
    Richard Fan & 8\\
    Mitchell Hynes & 8\\
    Rafeed Iqbal & 6\\
    Akshit Gulia & 7\\
    \bottomrule
  \end{tabular}
\end{table}

There is no exact number, but many of our meetings end up being
unplanned or planned on very short notice, so it is understandable
that there will be a decent number of these where some group members
do not attend simply because we didn't give much heads up about the meeting.

\section{Supervisor/Stakeholder Meeting Attendance}

\begin{table}[H]
  \centering
  \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Meetings}\\
    \midrule
    Total & 4\\
    Kyle D'Souza & 4\\
    Richard Fan & 4\\
    Mitchell Hynes & 4\\
    Rafeed Iqbal & 2\\
    Akshit Gulia & 4\\
    \bottomrule
  \end{tabular}
\end{table}

Rafeed had a previously discussed conflict for 1 of these meetings.

\section{Lecture Attendance}

\begin{table}[H]
  \centering
  \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Lectures}\\
    \midrule
    Total & 2\\
    Kyle D'Souza & 0\\
    Richard Fan & 2\\
    Mitchell Hynes & 2\\
    Rafeed Iqbal & 0\\
    Akshit Gulia & 1\\
    \bottomrule
  \end{tabular}
\end{table}

Kyle had a previously discussed conflict for one of these lectures.

\section{TA Document Discussion Attendance}

\begin{table}[H]
  \centering
  \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Lectures}\\
    \midrule
    Total & 1\\
    Kyle D'Souza & 1\\
    Richard Fan & 1\\
    Mitchell Hynes & 1\\
    Rafeed Iqbal & 1\\
    Akshit Gulia & 1\\
    \bottomrule
  \end{tabular}
\end{table}

\section{Commits}

\begin{table}[H]
  \centering
  \begin{tabular}{lll}
    \toprule
    \textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
    \midrule
    Total & 215 & 100\% \\
    Kyle D'Souza & 68 & 31.6\% \\
    Richard Fan & 35 & 16.3\% \\
    Mitchell Hynes & 32 & 14.9\% \\
    Rafeed Iqbal & 59 & 27.4\% \\
    Akshit Gulia & 21 & 9.8\% \\
    \bottomrule
  \end{tabular}
\end{table}

These numbers were obtained from looking at the GitHub contributor
insights and subracting the numbers from the POC demo team contribution report.
There is technically some overlap here between commits before the
POC, and commits after, but it should be minimal and only stuff not
included in that report.

\section{Issue Tracker}

\begin{table}[H]
  \centering
  \begin{tabular}{lll}
    \toprule
    \textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
    \midrule
    Kyle D'Souza & 55 & 17 \\
    Richard Fan & 5 & 16 \\
    Mitchell Hynes & 19 & 9 \\
    Rafeed Iqbal & 0 & 9 \\
    Akshit Gulia & 13 & 10 \\
    \bottomrule
  \end{tabular}
\end{table}

These numbers were obtained by taking the current numbers over the
whole existence of the repo and subtracting the numbers from the
previous team contribution report.
There may be a small amount of overlap from before the POC demo as a
result of that.

In terms of issues authored the reason it is so imbalanced is because
generally when assigning work for a deliverable we will all have a
call and Kyle will create issues and assign them to people (but
  we are all agreeing on whats being created and who its being assigned
to). To our knowledge issues can't be co-authored, so it leads to
that disproportionate issue creation statistic.

\section{CICD}

We will use Github Actions to run unit tests and linters on the
project on every pull request, to ensure consistency of code
formatting and that code added in a pull request does not break the
functionality of our application. This action currently exists for
our backend code, but nothing yet for the frontend.

There will also be a build and deploy action for deploying our application
into its development and production environments.

Currently we also have a GitHub action for checking the formatting of
our LaTeX documents.

\section{Additional Metrics}

\subsection{Pull Request (PR) Merges}

\begin{table}[H]
  \centering
  \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{PR's Merged}\\
    \midrule
    Total & 45\\
    Kyle D'Souza & 18\\
    Richard Fan & 10\\
    Mitchell Hynes & 5\\
    Rafeed Iqbal & 6\\
    Akshit Gulia & 6\\
    \bottomrule
  \end{tabular}
\end{table}

Similar to previous statistics, this one was taken by looking at the
current number of PR's merged, and subtracting the number we had in
the previous team contribution survey, which again has some overlap
with the time before the POC.

This metric takes into account the number of pull requests merged
that a student authored. It can be put off a bit if someone took over
a pull request after it was authored, but our team has not done this
very much, so the statistic should be accurate.

\subsection{Pull Request (PR) Reviews}

\begin{table}[H]
  \centering
  \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{PR's Reviewed}\\
    \midrule
    Kyle D'Souza & 25\\
    Richard Fan & 26\\
    Mitchell Hynes & 3\\
    Rafeed Iqbal & 2\\
    Akshit Gulia & 1\\
    \bottomrule
  \end{tabular}
\end{table}

Similar to previous statistics, this one was taken by looking at the
current number of PR's reviewed, and subtracting the number we had in
the previous team contribution survey, which again has some overlap
with the time before the POC.

This metric takes into account the number of pull requests reviewed
by a student which they did not author. The reason for disclusion of
pull requests the student authored is that often reviews by a student
on their own pull request is just responding to a comment, or putting
a small annotation, which is helpful, but is not what we are trying
to gather from this metric.

\end{document}
