\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
  colorlinks,
  citecolor=black,
  filecolor=black,
  linkcolor=red,
  urlcolor=blue
}
\usepackage{longtable}
\usepackage[round]{natbib}

\input{../Comments}
\input{../Common}

\begin{document}

\title{Verification and Validation Report: \progname}
\author{\authname}
\date{\today}

\maketitle

\pagenumbering{roman}

\section{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
  \toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
  \midrule
  Date 1 & 1.0 & Notes\\
  Date 2 & 1.1 & Notes\\
  \bottomrule
\end{tabularx}

~\newpage

\section{Symbols, Abbreviations and Acronyms}

Refer to \textit{Section 4: Naming Conventions and Terminology} of
the Software Requirements Specification document
\href{https://github.com/Spitgranger/SyncMaster/blob/main/docs/SRS-Volere/SRS.pdf}{SRS.pdf}.

\newpage

\tableofcontents

\listoftables %if appropriate

\listoffigures %if appropriate

\newpage

\pagenumbering{arabic}

This document ...

\section{Functional Requirements Evaluation}

\section{Nonfunctional Requirements Evaluation}

\subsection{Usability}
Usability testing was conducted on the application prototype to
validate humanity, look and feel, operational, and cultural requirements.
Two users were given the following scenarios for the usability test,
to simulate a typical use of the system:\\
\\
\textbf{Phase 1: Testing the contractor portal}
\\\\
You are a contractor hired by the City of Hamilton to perform work at a station.
You arrive and scan the QR code at the station to authenticate your
presence and explain the work you will perform.
We will ask you to perform a variety of tasks to assess their
discoverability and usability.
We welcome you explaining your thought process as you navigate
through the screens.
\begin{itemize}
  \item You have scanned the QR code. Please follow the initial steps
    for the health and safety acknowledgements. Did the experience of
    viewing the acknowledgements screen feel easy and intuitive? Did
    you encounter any errors?
    After the acknowledgements, are you able to find the station documents?
  \item Are you able to find and fill out the instructions for the
    purpose of your visit?
\end{itemize}
\textbf{Phase 2: Testing the admin portal}
\\\\
You are a Facility Manager who has an account with admin permissions.
You sign into the application and would like to perform some routine
tasks during the day.
\begin{itemize}
  \item You would like to navigate to the station documents and add a
    site specific document for station HC057. Please attempt to do
    so. Were you frustrated trying to find where this was located?
  \item Please locate the site wide documents which would be
    displayed for all stations.
  \item Please locate and view the site visit logs.
\end{itemize}
2 Users were then directed to fill out the Usability Survey
identified in the VnV Plan.\\
User 1: Man between the ages of 60 - 65, no prior experience with the
system. User is comfortable using a smartphone and laptop.\\
User 2: Woman between ages of 60 - 65, no prior experience with the
system. User is comfortable using a smartphone and laptop.
Through these actions, the following results were observed:\\
\begin{longtable}{|m{2cm}|m{1.5cm}|m{9cm}|}
  \hline
  \textbf{Test. ID}  & \textbf{User} & \textbf{Result} \\
  \hline
  TC-EU-1 & User 1& User successfully understood the distinction
  between the contractor and admin user. User experienced minor
  confusion what should be entered in the work order field, due to no
  real work order in scenario. User succesfully navigated core
  features of contractor
  and admin portal without issue. Test passed.\\
  \hline
  TC-EU-1 & User 2& User successfully navigated to contractor portal.
  Minor difficulties understanding distinction of site wide and
  site and site specific documentation on the admin portal,
  emphasizing the emportance of user documentation in requirement MS-SUP-1.
  Confusion did not hinder accessing all features of admin portal.
  Test passed.\\
  \hline
  TC-EU-2 & User 1& As an admin user, the tester was able to add a
  site wide document but did not receive a warning before deleting file
  thus identifying a bug in the system to be patched for rev1. Test failed.\\
  \hline
  TC-EU-2 & User 2& As an admin user, the tester was able to add a
  site wide document but did not receive a warning before deleting file
  thus identifying a bug in the system to be patched for rev1, same
  as issue identified for User 1. Test failed.\\
  \hline
  TC-LR-1 & User 1& User successfully discovered the documentation
  page. Did not have issues with selecting documents and
  rated their confidence as an 8. Test passed. \\
  \hline
  TC-LR-1& User 2& User successfully discovered the documentation
  page. Experienced minor confusion that documents are downloaded
  and not viewed in the application, but successfully opened the
  document. User gave their confidence a rating of 7. Test passed.\\
  \hline
  TC-LR-2 & User 1 & \textit{No onboarding documentation yet, user
  documentation to be taught on Mar 14} \\
  \hline
  TC-LR-2 & User 2 & \textit{No onboarding documentation yet, user
  documentation to be taught on Mar 14}\\
  \hline
  TC-UP-1 & User 1& User did not report anything offensive or
  political through all pages of the system. Test passed.\\
  \hline
  TC-UP-1 & User 2& User did not report anything offensive or
  political through all pages of the system. Test passed.\\
  \hline
  TC-UP-2 & User 1& User did not encounter any system errors during
  use. Test passed.\\
  \hline
  TC-UP-2 & User 2& User did not encounter any system errors during
  use. Test passed.\\
  \hline
  TC-AS-1 & User 1& The user reported that accessibility of the
  application felt similar to the City of Hamilton's main website
  when asked to compare the two. They rated their accessibility
  features to be comparable with a rating of 9 out of 10. Test passed.\\
  \hline
  TC-AS-1 & User 2& The user reported that the accessibility of the
  application felt similar to the City of Hamilton's main
  website when asked to compare the two. They rated the accessibility
  features of the application to be comparable with a rating
  of 8 out of 10. Test passed.\\
  \hline
  TC-LF-1 & User 1& User reported that the colour palette of the
  application did not cause them any issues and it was quite simple.
  They appreciated that the main colours are white and blue and that
  the application did not have many distractions. Rated as a 10 out of 10.
  Test passed.\\
  \hline
  TC-LF-1 & User 2& User reported that the colour palette of the
  application did not cause them any issues.
  Reported that some of the text on the Admin site visit logs was
  small and would be difficult to read without their glasses.
  Rated as an 8 out of 10 overall. Test passed.\\
  \hline
  TC-LF-2 & User 1& User was able to repeat the actions asked of them
  at the beginning of this section on an iPhone 8 and Samsung Galaxy A13
  for the contractor portal. User was able to use a Google Chrome and
  Microsoft Edge Browser on a Windows 10 operating system. Test passed.\\
  \hline
  TC-LF-2 & User 2& User was able to repeat the actions asked of them
  at the beginning of this section on an iPhone 13 and Samsung Galaxy A13
  for the contractor portal. User was able to use a Google Chrome and
  Microsoft Edge Browser on a Windows 10 operating system. Test passed.\\
  \hline
  TC-CR-1 & User 1& User did not feel the application violated any of
  the corporate pillars. Test passed.\\
  \hline
  TC-CR-1 & User 2& User did not feel the application violated any of
  the corporate pillars. Test passed.\\
  \hline
  TC-OE-1 & User 1 & User was able to access the application from
  their homes without issue. Test passed.\\
  \hline
  TC-OE-1 & User 2& User was able to access the application from
  their homes without issue. Test passed.\\
  \hline
  TC-OE-2 & User 1& User was successfully able to navigate the menus
  freely and reported a similar experience on both iOS
  and Android operating systems. Test passed.\\
  \hline
  TC-OE-2 & User 2& User reported feeling a similar experience across
  applications. Noted they preferred the experience on
  iPhone over Android because they are more familiar with the iOS
  interface than an Android interface. Test passed.\\
  \hline
  \caption{Usability Test Cases}
\end{longtable}
Most of the usability tests were successful, a promising sign for the
rev1 prototype. These initial tests did reveal some overlap in test cases
and missing survey questions which will be used to refine the
Usability Study further before it will be submitted in the Extras folder.

\subsection{Performance}

\begin{longtable}{|m{2cm}|m{5cm}|m{4cm}|m{4cm}|}
  \hline
  \textbf{Test. ID} & \textbf{Input} & \textbf{Expected Output} &
  \textbf{Result} \\
  \hline
  TC-PR-1 & User tries to retrieve a document & Average time for
  retrieving the documents should not exceed 2
  seconds & Pass, this is checked by
  manually loading 15 documents and taking the average of the times taken
  to retrieve them\\ \hline
  TC-PR-2 & User clicks on a UI element & Process user
  input within 2 seconds to minimize frustration. & Pass, this is checked by
  manually clicking on all UI elements and then measuring the time taken to
  see a response\\ \hline
  TC-PR-3 & Upload/Download a document & Document should be verified for
  integrity during upload and retrieval & Pass\\ \hline
  TC-PR-4 & Unauthorized user tries to access a document &
  Unauthorized user should not be allowed to access the document &
  Pass, this is verified by trying to upload/download a document
  without a valid access token or role\\ \hline
  TC-PR-5 & Search query for documents or user data & Search Resuls
  should be 95\% relevant to the input query & Pass\\ \hline
  TC-PR-7 & An unexpected input/event & System should handle the
  unexpected input/event gracefully and should not crash & Pass\\ \hline
  TC-PR-10 & Manually upload files of sizes 25MB, 50MB, 100MB, 250MB,
  500MB 1GB, and 2GB  & System should accept individual file sizes
  upto 1GB & Pass \\ \hline
  TC-PR-11 & Manually create nested documents/files & System should
  allow documents/folders to be nested &
  Pass\\ \hline
  \caption{Performance Test Cases}
\end{longtable}

\subsection{Maintainability and Support}

\begin{longtable}{|m{2cm}|m{1cm}|m{6cm}|m{3cm}|}
  \hline
  \textbf{Test. ID} & \textbf{Input} & \textbf{Expected Output} &
  \textbf{Result} \\
  \hline
  TC-MS-4 & - & There is 95\% line coverage and 90\% branch coverage
  on our code & Pass, this is being checked in GitHub actions\\ \hline
  TC-MS-5 & - & All functional requirements have a corresponding unit
  test & Pass\\ \hline
  TC-MS-6 & - & Contribution guidelines and maintainer documentation
  of system approved by the City of Hamilton & Fail, not yet approved\\ \hline
  TC-MS-7 & - & User manual exists and has been approved by the City
  of Hamilton & Fail, not yet created\\ \hline
  TC-MS-8 & - & OAS3 compliant documentation has been provided for
  all API's & Fail, not yet created\\ \hline
  TC-MS-9 & - & Internal abstractions (classes and functions) in the
  system have documentation associated with them & Pass, linter
  checks this\\ \hline
  TC-MS-10 & - & Documentation for deployment of the system exists &
  Fail, not yet created\\ \hline
  \caption{Maintainability and Support Test Cases}
\end{longtable}

\subsection{etc.}

\section{Comparison to Existing Implementation}

This section will not be appropriate for every project.

\section{Unit Testing}

Note: Unit tests all use \href{https://pypi.org/project/moto/}{moto}
to mock AWS services.

\subsection{Database Interaction Module Unit Tests}

\begin{longtable}{|m{2cm}|m{10cm}|m{1.4cm}|}
  \hline
  \textbf{Test. ID} & \textbf{Description} & \textbf{Result} \\ \hline
  UT-DB1 & Use the DBTable.put method to create an item, and check
  that it exists in the database afterwards & Pass\\ \hline
  UT-DB2 & Use the DBTable.put method with a failing precondition,
  and check that a ConditionCheckFailed is raised, and the item is
  not created & Pass\\ \hline
  UT-DB3 & Use the DBTable.put method with a permission error from
  AWS, and check that a PermissionException is raised, and the item
  is not created & Pass\\ \hline
  UT-DB4 & Use the DBTable.put method with an arbitrary error from
  AWS, and check that a ExternalServiceException is raised, and the
  item is not created & Pass\\ \hline
  UT-DB5 & Use the DBTable.get method to get a pre-existing item &
  Pass\\ \hline
  UT-DB6 & Use the DBTable.get method to get an item which does not
  exist, and check that a ResourceNotFound is raised & Pass\\ \hline
  UT-DB7 & Use the DBTable.get method with an arbitrary error from
  AWS, and check that a ExternalServiceException is raised & Pass\\ \hline
  UT-DB8 & Use the DBTable.delete method on a pre-existing item, and
  check that the item is no longer in the database & Pass\\ \hline
  UT-DB9 & Use the DBTable.delete method with a failing
  precondition, and check that a ConditionCheckFailed is raised, and
  the item is not deleted & Pass\\ \hline
  UT-DB10 & Use the DBTable.delete method with a permission error
  from AWS, and check that a PermissionException is raised, and the
  item is not deleted & Pass\\ \hline
  UT-DB11 & Use the DBTable.delete method with an arbitrary error
  from AWS, and check that a ExternalServiceException is raised, and
  the item is not deleted & Pass\\ \hline
  UT-DB12 & Use the DBTable.update method to update an item adding
  new attributes, and modifying existing ones, and check that these
  changes are reflected in the database & Pass\\ \hline
  UT-DB13 & Use the DBTable.update method to update an item removing
  some attributes and check that these changes are reflected in the
  database & Pass\\ \hline
  UT-DB14 & Use the DBTable.update method with a failing
  precondition, and check that a ConditionCheckFailed is raised, and
  the item is not updated & Pass\\ \hline
  UT-DB15 & Use the DBTable.update method with a permission error
  from AWS, and check that a PermissionException is raised, and the
  item is not updated & Pass\\ \hline
  UT-DB16 & Use the DBTable.update method with an arbitrary error
  from AWS, and check that a ExternalServiceException is raised, and
  the item is not updated & Pass\\ \hline
  UT-DB17 & Use the DBTable.query method, and ensure the returned
  items all match the query criterion & Pass\\ \hline
  UT-DB18 & Use the DBTable.query method, under a different GSI, and
  ensure the returned items all match the query criterion & Pass\\ \hline
  UT-DB19 & Use the DBTable.query method, with a reversed query
  direction, and ensure the returned items all match the query
  criterion & Pass\\ \hline
  UT-DB20 & Use the DBTable.query method, with using the start\_key
  of an existing db item, to determine where to start the query from,
  and ensure the returned items all match the query criterion & Pass\\ \hline
  UT-DB21 & Use the DBTable.query method, using a filter expression
  alongside a key condition, and ensure the returned items all match
  the query criterion & Pass\\ \hline
  UT-DB22 & Use the DBTable.query method, with an invalid key
  condition, and ensure that a ConditionValidationError is raised &
  Pass\\ \hline
  UT-DB23 & Use the DBTable.query method with an arbitrary error
  from AWS, and check that a ExternalServiceException is raised & Pass\\ \hline
  \caption{Unit Test Cases for Database Interaction Module}
\end{longtable}

\subsection{File Storage Interaction Module Unit Tests}

\begin{longtable}{|m{2cm}|m{10cm}|m{1.4cm}|}
  \hline
  \textbf{Test. ID} & \textbf{Description} & \textbf{Result} \\ \hline
  UT-FS1 & Use the S3Bucket.create\_upload\_url method to create an
  upload url, upload some content to the url, and check that the
  content exists in the S3 bucket & Pass\\ \hline
  UT-FS2 & Use the S3Bucket.create\_upload\_url method with a
  S3Bucket object that does not have write permissions, and check
  that a PermissionException gets raised & Pass\\ \hline
  UT-FS3 & Use the S3Bucket.create\_get\_url method for a
  pre-existing file in S3, and check that the file content can be
  accessed through the url, and check that a PermissionException gets
  raised & Pass\\ \hline
  UT-FS4 & Use the S3Bucket.delete method on a pre-existing file in
  S3, and check that the file no longer exists & Pass\\ \hline
  UT-FS5 & Use the S3Bucket.delete method on a pre-existing file in
  S3, with an ETag mismatch, and check that a ResourceNotFound is
  raised & Pass\\ \hline
  UT-FS6 & Use the S3Bucket.delete method with a permission error,
  and check that a PermissionException is raised & Pass\\ \hline
  UT-FS7 & Use the S3Bucket.delete method with an arbitrary error
  from AWS, and check that a ExternalServiceException is raised & Pass\\ \hline
  \caption{Unit Test Cases for File Storage Interaction Module}
\end{longtable}

\subsection{Location Verification Module Unit Tests}

\begin{longtable}{|m{2cm}|m{10cm}|m{1.4cm}|}
  \hline
  \textbf{Test. ID} & \textbf{Description} & \textbf{Result} \\ \hline
  UT-LV1 & Use the verify\_location method to verify a coordinate
  within a defined radius, and ensure the return value is True & Pass\\ \hline
  UT-LV2 & Use the verify\_location method to verify a coordinate
  outside a defined radius, and ensure the return value is False & Pass\\ \hline
  UT-LV3 & Use the verify\_location method to verify a coordinate
  just on the boundary of a defined radius, and ensure the return
  value is True & Pass\\ \hline
  \caption{Unit Test Cases for Location Verification Module}
\end{longtable}

\subsection{User Authentication Module Unit Tests}

\begin{longtable}{|m{2cm}|m{10cm}|m{1.4cm}|}
  \hline
  \textbf{Test. ID} & \textbf{Description} & \textbf{Result} \\ \hline
  UT-UA1 & Attempt to authenticate with a pre-existing user, and
  ensure that a token is successfully generated & Pass\\ \hline
  UT-UA2 & Attempt to authenticate with an invalid location, and
  ensure that an UnauthorizedException is raised & Pass\\ \hline
  UT-UA3 & Attempt to authenticate with an initial one-time
  password, and ensure that an ForceChangePasswordException is raised
  & Pass\\ \hline
  UT-UA4 & Attempt to authenticate with the wrong password, and
  ensure that an UnauthorizedException is raised & Pass\\ \hline
  UT-UA5 & Attempt to authenticate with a user that does not exist,
  and ensure that a ResourceNotFound is raised & Pass\\ \hline
  UT-UA6 & Attempt to authenticate with an arbitrary error from AWS,
  and ensure that a ExternalServiceException is raised & Pass\\ \hline
  UT-UA7 & Attempt to signout a user, with a valid access token, and
  ensure that the token is successfully invalidated & Pass\\ \hline
  UT-UA8 & Attempt to signout a user, with an invalid access token,
  and ensure that a BadRequestException is raised & Pass\\ \hline
  UT-UA9 & Attempt to signout a user, with an arbitrary error from
  AWS, and ensure that a ExternalServiceException is raised & Pass\\ \hline
  \caption{Unit Test Cases for User Authentication Module}
\end{longtable}

\subsection{User Management Module Unit Tests}

\begin{longtable}{|m{2cm}|m{10cm}|m{1.4cm}|}
  \hline
  \textbf{Test. ID} & \textbf{Description} & \textbf{Result} \\ \hline
  UT-UM1 & Create an admin, employee, and contractor account, using
  admin credentials & Pass\\ \hline
  UT-UM2 & Create a user, using admin credentials, where there is
  already another user using the same email, and check that a
  ConflictException is raised & Pass\\ \hline
  UT-UM3 & Create a user, using employee and contractor credentials,
  and ensure an UnauthorizedException is raised & Pass\\ \hline
  UT-UM4 & Create a user, with an arbitrary error occuring from AWS,
  and check that an ExternalServiceException is raised & Pass\\ \hline
  UT-UM5 & Get the details of an existing user, using admin and
  employee credentials & Pass\\ \hline
  UT-UM6 & Get the details of a user that does not exist, using
  admin and employee credentials, and ensure a ResourceNotFound is
  raised & Pass\\ \hline
  UT-UM7 & Use contractor credentials to get the details of their
  own user & Pass\\ \hline
  UT-UM8 & Use contractor credentials to get the details of another
  user, and ensure an UnauthorizedException is raised & Pass\\ \hline
  UT-UM9 & Get the details of a user, with an arbitrary error
  occuring from AWS, and check that an ExternalServiceException is
  raised & Pass\\ \hline
  UT-UM10 & Update a user, using admin credentials & Pass\\ \hline
  UT-UM11 & Update a user, using admin credentials, where the user
  to update does not exist, and check that a ResourceNotFound is
  raised & Pass\\ \hline
  UT-UM12 & Update a user, using employee and contractor
  credentials, and ensure an UnauthorizedException is raised & Pass\\ \hline
  UT-UM13 & Update a user, with an arbitrary error occuring from
  AWS, and check that an ExternalServiceException is raised & Pass\\ \hline
  UT-UM14 & Delete a user, using admin credentials & Pass\\ \hline
  UT-UM15 & Delete a user, using admin credentials, where the user
  to delete does not exist, and check that a ResourceNotFound is
  raised & Pass\\ \hline
  UT-UM16 & Delete a user, using employee and contractor
  credentials, and ensure an UnauthorizedException is raised & Pass\\ \hline
  UT-UM17 & Delete a user, with an arbitrary error occuring from
  AWS, and check that an ExternalServiceException is raised & Pass\\ \hline
  \caption{Unit Test Cases for User Management Module}
\end{longtable}

\subsection{Logging Module Unit Tests}

\begin{longtable}{|m{2cm}|m{10cm}|m{1.4cm}|}
  \hline
  \textbf{Test. ID} & \textbf{Description} & \textbf{Result} \\ \hline
  UT-LG1 & Create a site visit log, and ensure it gets added to the
  database & Pass\\ \hline
  UT-LG2 & Create a site visit log, with the same site id, user id,
  and entry time as an existing log, and ensure a ResourceConflict is
  raised & Pass\\ \hline
  UT-LG3 & Add an exit time to an existing log with no logged exit
  time, and ensure the change is reflected in the database & Pass\\ \hline
  UT-LG4 & Add an exit time to an existing log with no logged exit
  time, but an entry time prior to the exit time we are attempting to
  add, and ensure a TimeConsistencyException is raised & Pass\\ \hline
  UT-LG5 & Add an exit time to an existing log with a logged exit
  time, and ensure an ExitTimeConflict is raised & Pass\\ \hline
  UT-LG6 & Add an exit time, where there are no existing logs for
  the user at the given site, and ensure an ResourceNotFound is
  raised & Pass\\ \hline
  UT-LG7 & Get a list of all site visit logs, using admin and
  employee credentials & Pass\\ \hline
  UT-LG8 & Get a list of all site visit logs, using contractor
  credentials, and ensure that an UnauthorizedException is raised &
  Pass\\ \hline
  UT-LG9 & Get a list of all site visit logs using filters to only
  include logs modified between two given dates, and ensure that logs
  are correctly filtered & Pass\\ \hline
  UT-LG10 & Get a list of all site visit logs using a database
  start\_key to start the listing from a certain log, and ensure that
  logs start from the correct location & Pass\\ \hline
  \caption{Unit Test Cases for Logging Module}
\end{longtable}

\subsection{Document Management Module Unit Tests}

\begin{longtable}{|m{2cm}|m{10cm}|m{1.4cm}|}
  \hline
  \textbf{Test. ID} & \textbf{Description} & \textbf{Result} \\ \hline
  UT-DM1 & Create a document, and ensure it gets added to the
  database with the correct information & Pass\\ \hline
  UT-DM2 & Create a document with the name parent folder and document names as
  an existing document and check that a ResourceConflict is raised &
  Pass\\ \hline
  UT-DM3 & Get a single document for a particular site id and parent
  folder & Pass\\ \hline
  UT-DM4 & Get a list of documents including both files and folders for a
  particular site id and parent folder & Pass\\ \hline
  UT-DM5 & Get a list of documents for a site id and folder that has no
  documents and ensure that an empty list is returned & Pass\\ \hline
  UT-DM6 & Generate a presigned url that is used to upload a binary file to
  Amazon S3 give a particular S3 key & Pass\\ \hline
  UT-DM7 & Delete an existing file for a given site id and parent folder given
  that the file exists & Pass\\ \hline
  UT-DM8 & Delete a document of type folder that has with documents
  inside for a given site id
  and parent folder and ensure that both the folder and its contents are
  recursively deleted & Pass\\ \hline
  \caption{Unit Test Cases for Logging Module}
\end{longtable}

\section{Changes Due to Testing}

\wss{This section should highlight how feedback from the users and from
  the supervisor (when one exists) shaped the final product.  In particular
  the feedback from the Rev 0 demo to the supervisor (or to potential users)
should be highlighted.}

\section{Automated Testing}
N/A, the only automated testing we have is the unit tests.

\section{Trace to Requirements}

\begin{longtable}{|l|l|}
  \hline
  \textbf{Req. ID} & \textbf{Test ID's} \\
  \hline
  FR1 & TC-FR1, TC-FR2, UT-DM1\\ \hline
  FR3 & TC-FR3, UT-UM3\\ \hline
  FR4 & TC-FR4, UT-LG7\\ \hline
  FR5 & TC-FR5, UT-UA2\\ \hline
  FR6 & TC-FR6, UT-DM1\\ \hline
  FR7 & TC-FR8, UT-DM4, UT-DM6\\ \hline
  FR8 & TC-FR7\\ \hline
  FR9 & TC-FR9\\ \hline
  LF-AP1 & TC-LF-1 \\ \hline
  LF-ST1 & TC-LF-2 \\ \hline
  UH-EU1 & TC-EU1\\ \hline
  UH-EU2 & TC-EU2\\ \hline
  UH-LR1 & TC-LR1\\ \hline
  UH-LR2 & TC-LR2\\ \hline
  UH-UP1 & TC-UP1\\ \hline
  UH-UP2 & TC-UP2\\ \hline
  UH-AS1 & TC-AS1\\ \hline
  PR-SL1 & TC-PR-1\\ \hline
  PR-SL3 & TC-PR-2\\ \hline
  PR-SC1 & TC-PR-3\\ \hline
  PR-SC2 & TC-PR-4\\ \hline
  PR-PA1 & TC-PR-5\\ \hline
  PR-RFT1 & TC-PR-7\\ \hline
  PR-CR2 & TC-PR-10\\ \hline
  PR-SE1 & TC-PR-11\\ \hline
  OE-PE1 & TC-OE-1 \\ \hline
  OE-WE1 & TC-OE-2 \\ \hline
  OE-WE2 & TC-OE-2 \\ \hline
  OE-REL1 & TC-OE-4 \\ \hline
  OE-REL2 & TC-OE-4 \\ \hline
  OE-REL3 & TC-OE-4 \\ \hline
  OE-REL4 & TC-OE-4 \\ \hline
  MS-MTN4 & TC-MS-4 \\ \hline
  MS-MTN5 & TC-MS-5 \\ \hline
  MS-MTN6 & TC-MS-6 \\ \hline
  MS-SUP1 & TC-MS-7 \\ \hline
  MS-SUP2 & TC-MS-8 \\ \hline
  MS-SUP3 & TC-MS-9 \\ \hline
  MS-SUP4 & TC-MS-10 \\ \hline
  MS-ADP1 & TC-LF-2 \\ \hline
  MS-ADP2 & TC-LF-2 \\ \hline
  MS-ADP3 & TC-LF-2 \\ \hline
  SR-AR1 & TC-SS-1 \\ \hline
  SR-AR2 & TC-SS-1 \\ \hline
  SR-AR3 & TC-SS-1 \\ \hline
  SR-AR4 & TC-SS-2 \\ \hline
  SR-IR1 & TC-SS-2 \\ \hline
  SR-IR3 & TC-SS-4 \\ \hline
  SR-PR1 & TC-SS-5\\ \hline
  SR-AU1 & TC-SS-6 \\ \hline
  SR-IMR1 & TC-SS-7 \\ \hline
  SR-S1 & TC-SS-8 \\ \hline
  CR-CR1 & TC-CR-1 \\ \hline
  \caption{Requirements to Test Case Traceability Matrix}
\end{longtable}

\section{Trace to Modules}

Note: * indicates that any test prefixed with the test case ID,
covers the given module

\begin{longtable}{|l|l|}
  \hline
  \textbf{Module} & \textbf{Test ID's} \\
  \hline
  Database Interaction & UT-DB*\\ \hline
  Logging & UT-LG*\\ \hline
  File Storage & UT-FS*, TC-PR-10, TC-PR-11\\ \hline
  Location Verification & UT-LV*\\ \hline
  User Management & UT-UM*, TC-PR-5\\ \hline
  User Authentication & UT-AU*, TC-PR-4\\ \hline
  Document Management & UT-DM*, TC-PR-1, TC-PR-3, TC-PR-5\\ \hline
  \caption{Module to Test Case Traceability Matrix}
\end{longtable}

\section{Code Coverage Metrics}

The unit testing achieves 95\% line coverage and 90\% branch
coverage. This is checked by our GitHub Actions on every pull request.

\bibliographystyle{plainnat}
\bibliography{../../refs/References}

\newpage{}
\section*{Appendix --- Reflection}

The information in this section will be used to evaluate the team members on the
graduate attribute of Reflection.

\input{../Reflection.tex}

\begin{enumerate}
  \item What went well while writing this deliverable?
  \item What pain points did you experience during this deliverable, and how
    did you resolve them?
  \item Which parts of this document stemmed from speaking to your client(s) or
    a proxy (e.g. your peers)? Which ones were not, and why?
  \item In what ways was the Verification and Validation (VnV) Plan different
    from the activities that were actually conducted for VnV?  If there were
    differences, what changes required the modification in the plan?  Why did
    these changes occur?  Would you be able to anticipate these
    changes in future
    projects?  If there weren't any differences, how was your team
    able to clearly
    predict a feasible amount of effort and the right tasks needed to build the
    evidence that demonstrates the required quality?  (It is expected that most
    teams will have had to deviate from their original VnV Plan.)
\end{enumerate}

\end{document}
